Mergeable Types

### 2017-02-28 paper/meta.tex
Fig. added causal hist.

In a legal branching history, every version has a unique locus
(property follows from Def.~\ref{def:mergeability} below). We
define the \emph{causal history} of a version as the set of all
ancestors of that version. A locus ($v_o$) of a version ($v$) is
therefore the maximum element (lowest element in the ancestor
relation) of the causal history of $v$'s internal ancestor that was
the result of the last merge. We make use of this observation while
defining mergeability.

>>>>

\begin{wrapfigure}{l}{.4\textwidth}
\centering
\includegraphics[scale=0.6]{Figures/causal-history}
\caption{The cloud represents the set of all ancestors of versions $v_i$ and
$v_{i+1}$, i.e., their causal history. The locus $v_k$ of both is the
version that succeeds every other ancestor in the causal history.}
\label{fig:causal-history}
\end{wrapfigure}
In a legal branching history, every version has a unique locus
(property follows from Def.~\ref{def:mergeability} below). We define
the \emph{causal history} of a version as the set of all ancestors of
that version. A locus ($v_o$) of a version ($v$) is therefore the
maximum element (lowest element in the ancestor relation) of the
causal history of $v$'s internal ancestor that was the result of the
last merge. This is illustrated in Fig.~\ref{fig:causal-history}. We
make use of this observation while defining mergeability.
